---
title: Modeling Truck Safety Critical Events
subtitle: Efficient Bayesian Hierarchical Statistical and Reliability Models
author: Miao Cai
institute: Department of Epidemiology and Biostatistics
# date: "`r Sys.Date()`"
titlegraphic: './logos/SLU-CPHSJ-left.png'
fontsize: 10pt
output:
 beamer_presentation:
    template: tex/Beamer_Miao_template.tex
    keep_tex: false
    latex_engine: xelatex # pdflatex also works here
    dev: cairo_pdf # I typically comment this out  if latex_engine: pdflatex
    slide_level: 3
make149: true
mainfont: "Open Sans" # Try out some font options if xelatex
titlefont: "Titillium Web" # Try out some font options if xelatex
bibliography: [../bib/bib.bib]
csl: [../bib/numbered.csl]
---

```{r setup, include=FALSE, cache=F, message=F, warning=F, results="hide"}
knitr::opts_chunk$set(cache=FALSE,
                      out.width='80%',
                      out.height='80%',
                      out.extra='keepaspectratio')
#knitr::opts_chunk$set(fig.path='figs/')
```

### Dissertation committee

- Chair:
    + Steven E. Rigdon, PhD

- Committee Members:
    + Fadel Megahed, PhD
    + Hong Xian, PhD

- At-large Committee:
    + AA, PhD
    + BB, PhD
    
The problem
============

### Transportation

Transportation safety deserves attention:

- The 8-th leading cause of death globally in 2016, [@who2018]
- 1.4 million people killed, mostly aged 4 to 44 years old, [@who2018]
- 518 billion dollars. [@dalal2013economics]

Trucks are the backbone of the economy:

- 70% of freight delivered by trucks,
- 73.1% of value and 71.3% of domestic goods, [@olson2016weight; @anderson2017exploratory]

### Challenges for trucking industry

Drivers:

1. drive alone for long hours, 
2. work under time demands, challenging weather and traffic conditions,
2. sleep deprivation and disorder

Trucks: 

1. huge weights, 
2. large physical dimensions,
3. potentially carry hazardous cargoes.

### Truck crash studies

Traditional studies almost exclusively use data that ultimately trace back to **post hoc** __vehicle inspection__, __interviews__ with survived drivers and witnesses, and __police reports__. [@hickman2018synthetic; @stern2019data]

1. rare events $\rightarrow$ difficulty in estimation, [@theofilatos2018impact]
2. retrospective studies $\rightarrow$ recall bias, [@girotto2016professional]
3. crashes are underreported $\rightarrow$ selection bias. [@ye2011investigation; @savolainen2011statistical]

### Naturalistic driving studies (NDS)

> NDS uses **unobtrusive** devices, sensors, and cameras installed on vehicles to **proactively** collect frequent naturalistic driving behavior and performance data under **real-world driving** conditions [@hickman2018synthetic; @guo2019statistical]

1. driver-based data (compare rates),
2. high-resolution driver behavior and performance data,
3. less costly and difficult per observation.

### Safety critical events (SCEs)

SCEs are

>  a chain of adverse events following an initial off-nominal event, which can result in an accident if compounded with additional adverse conditions. [@saleh2013accident]

Examples of SCEs are: 

1. hard brakes,
2. headways,
3. rolling stability,
4. $\cdots$

### The problem

NDSs are relatively new and less studied. Here are several problems remained in NDS.

1. Are SCEs associated with real crashes among truck drivers?
2. Can we predict SCEs?
3. How can we innovate existing models to account for features of NDS?



Methods
=======

### The Good Day Hypothesis

We know the following about Ice Cube's day.

1. The Lakers beat the Supersonics.
2. No helicopter looked for a murder.
3. Consumed Fatburger at 2 a.m.
4. Goodyear blimp: "Ice Cube's a pimp."

### The Good Day Hypothesis

This leads to two different hypotheses:

- $H_0$: Ice Cube's day is statistically indistinguishable from a typical day.
- $H_1$: Ice Cube is having a good (i.e. greater than average) day.

These hypotheses are tested using archival data of Ice Cube's life.

### LaTex Equations

The likelihood function of a non-homogeneous Poisson process (NHPP) with a power law process (PLP) intensity function is:

\begin{equation}\label{eq:pdftau}
\begin{aligned}
f(n, t_1, t_2, \cdots, t_n) & = f(n)f(t_1, t_2, \cdots, t_n|n)\\
& = \frac{e^{-\int_0^\tau \lambda(u)du}[\int_0^\tau \lambda(u)du]^n}{n!}n!\frac{\prod_{i=1}^n\lambda(t_i)}{[\Lambda(\tau)]^n}\\
& = \Big(\prod_{i=1}^n\lambda(t_i) \Big)e^{-\int_0^\tau \lambda(u)du}\\
& = \Big(\prod_{i=1}^n\frac{\beta}{\theta}(\frac{t_i}{\theta})^{\beta - 1} \Big)e^{-(\tau/\theta)^\beta},\\ 
n & = 0, 1, 2, \cdots, \quad  0 < t_1 < t_2 < \cdots < t_n
\end{aligned}
\end{equation}

Results
=======

### Include figures

```{r jplp, fig.cap='The intensity function, SCEs, and rests of a jump-point PLP',echo=FALSE}
knitr::include_graphics("figs/PLP-jump-point-intensity.pdf")
```

### A Total Conflict Game Between Sheena Easton and Her Baby

|                        | XX            | YY            |
|------------------------|---------------|---------------|
| **Baby Home Again**    |  -100, **100**| **100**, 0    |
| **Baby Stays at Work** |   **50**, 0   | -100, **100** |

Sheena Easton and her baby are playing a **zero-sum (total conflict) game**.

- Akin to Holmes-Moriarty game (see: von Neumann and Morgenstern)
- Solution: **mixed strategy**


Conclusion
==========

### Python

Wonderful Python packages are available:

- `pandas`, 
- `numpy`, 
- `sci-kit`, 
- $\cdots$
- `keras`

### R

Wonderful R packages are available:

- `tidyverse`
- `data.table`
- `caret`

### The best language

> PHP is the best language.


### References
